---
title: "SuggestK Vignette"
author: "Victor Lee"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

The package crawls search terms from the major search engines in Korea; 
[daum](https://www.daum.net/), [naver](https://www.naver.com/) and [google](https://www.google.com/). The usage is straightforward.

1. select search engine function and run that function
    - daum: `daum_keyword()`
    - naver: `naver_keyword()`
    - google: `google_keyword()`
1. if you want to visualize search terms relationship, call `suggest_list2df())` function which will convert list data structure to dataframe.
1. call `visualize_suggest()` function which will transform native dataframe into network object automatically and visualize search term relationship; keyword, 1st search terms, and 2nd search terms. [networkD3](https://cran.r-project.org/web/packages/networkD3/index.html) is a main engine for the newtork visualization.

## Install 

You could install `suggestK` package through [Github](https://github.com/statkclee/suggestK).

``` {r install-suggestK}
devtools::install_github("statkclee/suggestK")
library(suggestK)
```

## Crawl Related Search Terms

### Daum

[daum](https://www.daum.net/) search engine provides very flexible related search results in that if a search term is not used frequently, it will return related keywrods quickly, but it could take a couple of minutes in some cases. 

`daum_keyword()` function returns list datatype such that it will be useful to see related keywords with the `jsonedit()` function in `listviewer` package.

In case of the multiple keyword such as "data scientist", you need to add `+` sign between two search keywords. Unless you add `+` sign, you will not get what you expect.
****

``` {r daum}
data_scientist <- daum_keyword("data+scientist")
str(data_scientist)
```

### Naver

[naver](https://www.naver.net/) search engine provides only 10 related keywords, which means that the search query can finish very quickly, but if you expect exhaustive related terms, it will give only partial keywords.

`naver_keyword()` function returns list datatype such that it will be useful to see related keywords with the `jsonedit()` function in `listviewer` package.

``` {r naver}
korea <- naver_keyword("korea")
str(korea)
```

### Google

[google](https://www.naver.net/) search engine provides only 10 related keywords such that google suggest query works really fast, but compared with Daum and Naver, **Google Suggest** works differently. You need to be careful when interpreting related terms.

`google_keyword()` function returns list datatype such that it will be useful to see related keywords with the `jsonedit()` function in `listviewer` package.

``` {r google}
korea <- google_keyword("korea")
```

## Convert list to dataframe

Once we have list data from the keyword search, it is necessary to convert list to dataframe. The subsequent data analysis, modeling, and visualization tasks prefer dataframe in most cases.

The `suggestK` package has two function for the same task because Korean and non-Korean search engines have different interfaces. `suggest_list2df()` function convert list from  NAVER and DAUM search terms to dataframe whereas `google_list2df()` function convert list from Google search terms to dataframe.

``` {r naver-daum-list2df}
suggest_list2df(data_scientist, "data+scientist")[[1]] %>% head()
```

In case of google, it works similarly.

``` {r google-list2df}
google_list2df(korea, "korea")[[1]] %>% head()
```

## Visualize

`visualize_suggest()` function enables to visualize Keyword, 1st Search Terms and 2nd Search Terms through `networkD3`.
To get visualized artefacts, pass the search term and search engine name to `visualize_suggest()` function which will automatically crawl search terms, convert data structure, visualize, and return the results.

``` {r visualize, fig.width=8, fig.height=8}
visualize_suggest("korea", "google")
```



